Gap formation and stability in non-isothermal protoplanetary discs

### 2015-03-27 paper/results.tex
revision 3

For fast cooling rates ($\tilde{\beta}\lesssim 1$), the
vortex lifetime is maximized for $\tilde{\beta}\to0$: we find 
$t_{\mathrm{life}} \approx 2100P_0$ for $\tilde{\beta}=0.01$ and 
decreases to $t_{\mathrm{life}} \approx 1100P_0$ for
$\tilde{\beta}=0.5$. {\bf Note that for very small $\tilde{\beta}$, 
  there is significant contribution to the overall vortex lifetime due
  to a long decay timescale. }
For longer cooling times ($\tilde{\beta}\gtrsim
1$) the vortex lifetimes maximizes at $\tilde\beta=2.5$ with 
$t_{\mathrm{life}}\approx 1650P_0$.  
%The other timescales $t_\mathrm{diss}$ and
%$t_\mathrm{Mach}$ are less complicated, but still display a
%non-monotonic dependence on $\tilde{\beta}$, with a single maximum at
%$\tilde{\beta}=1$.

>>>>

For fast cooling rates ($\tilde{\beta}\lesssim 1$), the
vortex lifetime is maximized for $\tilde{\beta}\to0$: we find 
$t_{\mathrm{life}} \approx 2100P_0$ for $\tilde{\beta}=0.01$ and 
decreases to $t_{\mathrm{life}} \approx 950P_0$ for
$\tilde{\beta}=0.25$. {\bf Note that for very small $\tilde{\beta}$, 
  there is significant contribution to the overall vortex lifetime due
  to a long decay timescale. }
For longer cooling times ($\tilde{\beta}\gtrsim
1$) the vortex lifetimes maximizes at $\tilde\beta=2.5$ with 
$t_{\mathrm{life}}\approx 1650P_0$.  
%The other timescales $t_\mathrm{diss}$ and
%$t_\mathrm{Mach}$ are less complicated, but still display a
%non-monotonic dependence on $\tilde{\beta}$, with a single maximum at
%$\tilde{\beta}=1$.
